---
title: "Alcohol vs Seat choice"
author: "Christina Jones"
date: "14 Sept 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??
$H_0$ There is no difference in alcohol consumption based on where one sits in class   


$H_1$ There is a difference in alcohol consumption based on where one sits in class
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

The box plot shows that people that students that sit in back drink more frequently the students that sit in the front and middle which are seemly the same. 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


This boxplot shows the same data of students in back row drink significantly more then the front and middle rows that show little difference. 


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The table shows that the mean (average) of students that sit in the back row is at 8.555. The students that sit in the front and middle do not exceed 3.33. These averages are very different. The students that sit in the back are much more likely to be alcohol consumers. 



## Inferential Tests  
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
```{r}
plot(TukeyHSD(model1))
```

We have a p value of 0.000116 so we conclude that we reject the $H_0$;there is a difference with where you sit and the alcohol that is consumed 


## Conclusions

People that sit in the back drink significantly more then those who sit in the middle or front of the class. We reject the NULL hypothesis because there is a difference in the amount of alcohol consumption with the students that sit in the back row. 


